The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 paper.tex
Move all theoretical part to SI

\subsection{Polarizability-Based Theoretical Model}
\todo[inline]{In case of Nat. Nanotechnol., I would like to move all
  theoretical information to SI}.
Based on the 2D polarizability, we
then theoretically investigate the potential existence of the
Moss-like relations for 2D materials.  Due to its highly anisotropic
nature, the wavefunction of an isolated 2D material $\psi(\mathbf{r})$
can be separated into the in- and out-of-plane components, similar to
the treatment of quantum wells (QW),\cite{davies_physics_1997} such
that $\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such
that $\psi=\psi^{\parallel}\psi^{\perp}$, where
$\boldsymbol{\rho}=(x, y)$ is the in-plane coordinate. Using the Bloch
theorem, the periodic $\psi^{\parallel}(\boldsymbol{\rho})$ can be
further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the limit that $L\to\infty$,
when $\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Combine this with
Eqs. \ref{eq:alpha-para-def}, \ref{eq:alpha-perp-def} and
\ref{eq:RPA-eps2}, and taking the difference between the properties of
in-plane and out-of-plane polarizabilities, we derive the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ under small perturbation
(details see Supplementary Section S4):
  \label{eq:alpha_para_RPA}
  & \alpha_{\mathrm{2D}}^{\parallel} &= \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
                         {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  \label{eq:alpha_perp_RPA}
  & \alpha_{\mathrm{2D}}^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
  \sum_{\mathrm{c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
where the integral is performed within the first Brillouin Zone (BZ)
in the reciprocal $\mathbf{k}$-plane. Although they only differ by the
numerator inside the integral, the distinct behaviors of $u(\rho)$
(periodic function) and $\psi(z)$ (confined to the 2D material) give
rise to the different relations of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
Eq. \ref{eq:alpha_para_RPA} is evaluated to be
$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
degeneracy associated with the minimal bandgap
\cite{Jiang_2017_Eg_Eb}. On the contrary, $\psi(z)$ is the solution to
the Schr\"{o}dinger equation with Hamiltonian
$\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where $\hbar$ is
the reduced Planck constant, $m_{e}$ is electron mass and $V(z)$ is
the confined Coulombic potential along the z-direction created by the
nuclei \cite{davies_physics_1997,ihn_semiconductor_2009}. Using a
simple particle-in-box model, we show that both the numerator and
denominator parts of Eq. \ref{eq:alpha_perp_RPA} are independent of
$E_{g}$ but instead modulated by the size of the potential confinement
(details see Supplementary Section S4). We further prove, using both
quantum mechanical and fundamental electrostatic models, that
$\alpha_{\mathrm{2D}}^{\perp}$ is actually proportional to the size of potential
confinement (details see Supplementary Section S4), which we may
relate with the thickness $\delta$ of the 2D material. Now we may
finally propose the 2D analog of the Moss relation with both in- and
out-of-plane polarizations:
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
which form the main conclusion of this work. Next, we will validate
the proposed 2D Moss-like relations using first principle
calculations.

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX). In fact, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

@@

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(details see Supplementary Section S3). Althought the dielectric
properties may be overestimated at PBE level due to underestimation of
the bandgap compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
with the linear coefficient very close to the HSE06 results. We have
also tested the potential relation between the 2D polarizabilities
with other physical quantities, including the effective carrier mass,
quantum capacitance and total atomic polarizabilities, while no
apparent correlations are found (details see Supplementary Section
S3).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

>>>>

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX \todo{note}). In fact, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

@@

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(details see Supplementary Section \ref{SI-sec:gpaw-1}). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals \cite{Van_Dyck_2017}, similar linear trends can be
observed for both $\alpha^{\parallel}_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}$, with the linear coefficient very close
to the HSE06 results (details see Supplementary Section
\ref{SI-sec:gpaw-2}). We have also tested the potential relation
between the 2D polarizabilities with other physical quantities,
including the effective carrier mass, quantum capacitance and total
atomic polarizabilities, while no apparent correlations are found
(details see Supplementary Section \ref{SI-sec:gpaw-3}).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure \ref{SI-fig:ellipsoid}). The polarizability ellipsoid for a 2D
material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}\todo{Lacks MoSe2}.  Moreover,
$r_{0}^{\parallel}$ is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.
